---
title: Tidymodels packages
format: 
  html:
    toc: true
    number-sections: true
    embed-resources: true
    css: ../css/styles.css
---

## Installation and use

### Install `tidymodels`

```{r}
#| eval: false
install.packages("tidymodels")
```

### Run `tidymodels`

```{r}
#| eval: false
library(tidymodels)
```

### Core tidymodels

Meta-package for modeling and statistical analysis that shares the underlying design philosophy, grammar, and data structures of the tidyverse.

#### Packages loaded on the startup


- [`broom`](https://broom.tidymodels.org/) takes the messy output of built-in functions in R, such as `lm`, `nls`, or `t.test`, and turns them into tidy data frames.

-   [`dials`](https://dials.tidymodels.org) has tools to create and manage values of tuning parameters.

-   [`dplyr`](https://dplyr.tidyverse.org) contains a grammar for data manipulation.

-   [`ggplot2`](https://ggplot2.tidyverse.org) implements a grammar of graphics.

-   [`infer`](https://infer.tidymodels.org) is a modern approach to statistical inference.

-   [`parsnip`](https://parsnip.tidymodels.org) is a tidy, unified interface to creating models.

-   [`purrr`](https://purrr.tidyverse.org) is a functional programming toolkit.

-   [`recipes`](https://recipes.tidymodels.org) is a general data preprocessor with a modern interface. It can create model matrices that incorporate feature engineering, imputation, and other help tools.

-   [`rsample`](https://rsample.tidymodels.org) has infrastructure for *resampling* data so that models can be assessed and empirically validated.

-   [`tibble`](https://tibble.tidyverse.org) has a modern re-imagining of the data frame.

-   [`tune`](https://tune.tidymodels.org) contains the 
functions to optimize model hyper-parameters.

-   [`workflows`](https://workflows.tidymodels.org) has methods to combine pre-processing steps and models into a single object.

-   [`yardstick`](https://yardstick.tidymodels.org) contains tools for evaluating models (e.g. accuracy, RMSE, etc.).

### Specialized packages

The tidymodels framework also includes many other packages designed for specialized data analysis and modeling tasks. They are not loaded automatically with `library(tidymodels)`.

#### Perform statistical analysis

-   [infer](https://infer.tidymodels.org/) is a high-level API for tidyverse-friendly statistical inference.

-   [corrr](https://corrr.tidymodels.org/) package has tidy interfaces for working with correlation matrices.

#### Create robust models

-   [spatialsample](http://spatialsample.tidymodels.org/) package provides resampling functions and classes like rsample, but specialized for spatial data.

-   [discrim](https://discrim.tidymodels.org/) contains definitions for discriminant analysis models.

-   [poissonreg](https://poissonreg.tidymodels.org/) provides definitions for Poisson regression models. 

-   [plsmod](https://plsmod.tidymodels.org/) enables linear projection models.

-   [rules](https://rules.tidymodels.org/) does the same for rule-based classification and regression models. 

-   [baguette](https://baguette.tidymodels.org/) creates ensemble models via bagging

-   [multilevelmod](https://multilevelmod.tidymodels.org/) provides support for multilevel models (otherwise known as mixed models or hierarchical models).

-   [embed](https://embed.tidymodels.org/) contains steps to create embeddings or projections of predictors. 

-   [textrecipes](https://textrecipes.tidymodels.org/) has extra steps for text processing.

-   [themis](https://themis.tidymodels.org/) can help alleviate class imbalance using sampling methods.

-   [tidypredict](https://tidypredict.tidymodels.org/) and [modeldb](https://modeldb.tidymodels.org/) can convert prediction equations to different languages (e.g. SQL) and fit some models in-database.

#### Tune, compare, and work with your models

-   [workflowsets](https://workflowsets.tidymodels.org/) lets you create sets of workflow objects for tuning and resampling.

-   [stacks](https://stacks.tidymodels.org/) package provides tools for stacked ensemble modeling.

-   [finetune](https://finetune.tidymodels.org/) package extends the tune package with more approaches such as racing and simulated annealing.

-   [usemodels](https://usemodels.tidymodels.org/) package creates templates and automatically generates code to fit and tune models.

-   [probably](https://probably.tidymodels.org/) has tools for post-processing class probability estimates.

-   [tidyposterior](https://tidyposterior.tidymodels.org/) package enables users to make formal statistical comparisons between models using resampling and Bayesian methods.

-   [butcher](https://butcher.tidymodels.org/) package can reduce the size of those objects by removing the sub-components.

-   [applicable](https://applicable.tidymodels.org/) can produce metrics that measure extrapolation. 

-   [shinymodels](https://shinymodels.tidymodels.org/) lets you explore tuning or resampling results via a Shiny app.

#### Develop custom modeling tools

-   [hardhat](https://hardhat.tidymodels.org/) is a *developer-focused* package that helps beginners create high-quality R packages for modeling. 
